---
title: 'Replication: Measurement and theory in legislative networks'
author: "Yaoyao Dai"
date: "February 8, 2016"
output: pdf_document
---

I first prepare and change the data sets into network objects following the author's replication code. I then plot the legislative cosponsorship network. I also visualize the party attributes with red representing republican and blue representing democrat. 

```{r, echo=FALSE, message=FALSE,warning=FALSE}
rm(list=ls())
options(scipen=4)
library(statnet)
library(foreign)
library(arm)
###data preparation
legs<-read.csv("~/Documents/Replication/tx_legislators.csv")
billvotes<-read.csv("~/Documents/Replication/tx_bill_votes.csv")
cosp<-read.csv("~/Documents/Replication/tx_bill_sponsors.csv")
rollcalls<-read.csv("~/Documents/Replication/tx_bill_legislator_votes.csv")

###Subset cosp network to lower chamber 81st 
unique.legs<-unique(cosp$leg_id)
cosp2<-subset(cosp, cosp$chamber=="lower" & cosp$session==81)
unique.bills<-unique(cosp2$bill_id)
#print(length(unique.bills))

###Generate blank Matrix
matrix3<-matrix(0, length(unique.legs), length(unique.legs))
row.names(matrix3)<-unique.legs
colnames(matrix3)<-unique.legs

###Fill in cross-chamber sponsor to author connections
for(i in 1:length(unique.bills)){
  cosp3<-subset(cosp2, cosp2$bill_id==unique.bills[i])	
  author<-match(cosp3$leg_id[which(cosp3$type=="author")], unique.legs)	
  sponsor<-match(cosp3$leg_id[which(cosp3$type=="sponsor")], unique.legs)	
  matrix3[sponsor, author]<-matrix3[sponsor, author]+1
  if(sum(cosp3$type=="sponsor")>1){print(unique.bills[i])}
}
#sum(matrix3>0)
###Subset cosp network to upper chamber 81st 
cosp2<-subset(cosp, cosp$chamber=="upper" & cosp$session==81)
unique.bills<-unique(cosp2$bill_id)
#print(length(unique.bills))

###Fill in cross-chamber sponsor to author connections
for(i in 1:length(unique.bills)){
  cosp3<-subset(cosp2, cosp2$bill_id==unique.bills[i])	
  author<-match(cosp3$leg_id[which(cosp3$type=="author")], unique.legs)	
  sponsor<-match(cosp3$leg_id[which(cosp3$type=="sponsor")], unique.legs)	
  matrix3[sponsor, author]<-matrix3[sponsor, author]+1
  #if(sum(cosp3$type=="sponsor")>1){print(unique.bills[i])}
}
#sum(matrix3>0)

########Add Party Vector
Party<-rep(NA, nrow(matrix3))
for(i in 1:length(Party)){
  if(length(which(legs$leg_id==row.names(matrix3)[i]))>0){
    Party[i]<-as.character(legs$party[which(legs$leg_id==row.names(matrix3)[i])])
  }
}

missing<-which(Party!="Democratic" & Party!="Republican" | is.na(Party)==TRUE)
missing2<-vector(mode="character", length=length(missing))
for(i in 1:length(missing)){
  missing2[i]<-as.character(cosp$name[which(cosp$leg_id==row.names(matrix3)[missing[i]])])[1]	
}

missing3<-rep("Republican", length=length(missing))
missing3[2]<-"Democratic"
missing3[3]<-"Democratic"
missing3[4]<-"Democratic"
missing3[6]<-"Democratic"
missing3[7]<-"Democratic"
missing3[8]<-"Democratic"
missing3[9]<-"Democratic"
missing3[10]<-"Democratic"
missing3[12]<-"Democratic"
missing3[14]<-"Democratic"
missing3[15]<-"Democratic"
missing3[20]<-"Democratic"
missing3[21]<-"Democratic"
missing3[24]<-"Democratic"
missing3[27]<-"Democratic"
missing3[28]<-"Democratic"
missing3[29]<-"Democratic"
missing3[30]<-"Democratic"
missing3[31]<-"Democratic"
missing3[32]<-"Democratic"
missing3[37]<-"Democratic"
missing3[38]<-"Democratic"
missing3[39]<-"Democratic"
missing3[35]<-"Democratic"
missing3[34]<-"Democratic"
missing3[40]<-"Democratic"
missing3[41]<-"Democratic"
missing3[42]<-"Democratic"
missing3[43]<-"Democratic"
missing3[44]<-"Democratic"
missing3[45]<-"Democratic"
missing3[46]<-"Democratic"
missing3[47]<-"Democratic"

#Party
for(i in 1:length(missing3)){
  Party[missing[i]]<-missing3[i]	
}
#Party
Party<-ifelse(Party=="Republican", 0, 1)


########Add Leadership Vector
Leadership<-rep(NA, nrow(matrix3))
for(i in 1:length(Leadership)){
  if(length(which(legs$leg_id==row.names(matrix3)[i]))>0){
    Leadership[i]<-as.character(legs$leadership[which(legs$leg_id==row.names(matrix3)[i])])
  }
}
Leadership<-ifelse(is.na(Leadership)==FALSE, as.numeric(Leadership), 0)

########Add Appropriations Vector
Appropriations<-rep(0, nrow(matrix3))
for(i in 1:length(Appropriations)){
  if(length(which(legs$leg_id==row.names(matrix3)[i]))>0){
    Appropriations[i]<-as.character(legs$Appropriations[which(legs$leg_id==row.names(matrix3)[i])])
  }
}
Appropriations<-as.numeric(Appropriations)

########Add Chamber Vector
Chamber<-rep(NA, nrow(matrix3))
for(i in 1:length(Appropriations)){
  if(length(which(legs$leg_id==row.names(matrix3)[i]))>0){
    Chamber[i]<-as.character(legs$chamber[which(legs$leg_id==row.names(matrix3)[i])])
  }
}
Chamber2<-ifelse(Chamber=="upper", 1, 0)
Chamber2[37]<-0
Chamber2[174]<-0

############Clear Matrix of within-chamber connections
ss<-which(Chamber2==1)
rr<-which(Chamber2==0)

#sum(matrix3>0)
matrix3[ss,ss]<-0
matrix3[rr,rr]<-0
#sum(matrix3>0)

########Add Rules Vector
Rules<-rep(0, nrow(matrix3))
for(i in 1:length(Rules)){
  if(length(which(legs$leg_id==row.names(matrix3)[i]))>0){
    Rules[i]<-as.character(legs$Rules[which(legs$leg_id==row.names(matrix3)[i])])
  }
}
Rules<-as.numeric(Rules)

######Rename Legislators from IDs to Names
leg.names<-vector(mode="character", length=length(Party))
for(i in 1:length(leg.names)){
  leg.names[i]<-as.character(cosp$name[which(cosp$leg_id==row.names(matrix3)[i])[1]])	
}

####Add Joint Committees
Joint.Comms<-numeric(length=nrow(matrix3))
for(i in 1:length(Joint.Comms)){
  if(length(which(legs$leg_id==row.names(matrix3)[i]))>0){	
    if(legs$Aging[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-1}
    if(legs$Criminal.Commitments[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-2}
    if(legs$Dyslexia[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-3}
    if(legs$Environmental.Flows[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-4}
    if(legs$Bexar[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-5}
    if(legs$Criminal.Justice[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-6}
    if(legs$Aquifer[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-7}
    if(legs$HHS[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-8}
    if(legs$Windstorm[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-9}
    if(legs$Finance.Weights[which(legs$leg_id==row.names(matrix3)[i])]==1){Joint.Comms[i]<-10}
  }		
  #print(i)
}
```



```{r, echo=FALSE, warning=FALSE}
###Set Network
Network<-network(matrix3)

###Add Attributes
set.vertex.attribute(Network, "Party", Party)
set.vertex.attribute(Network, "names", leg.names)
set.vertex.attribute(Network, "leadership", Leadership)
set.vertex.attribute(Network, "Rules", Rules)
set.vertex.attribute(Network, "Appropriations", Appropriations)
set.vertex.attribute(Network, "Chamber", Chamber2)
#set.vertex.attribute(Network, "SenDist", SenDist)
set.vertex.attribute(Network, "JointComms", Joint.Comms)

### plot
library(sna)
party_color<-c("red","blue")
vert.cols <- party_color[Party+1]
plot(Network,vertex.cex=1,edge.col=rgb(150,150,150,50,maxColorValue=255),vertex.col=vert.cols,main="Network of legislative cosponsorship")
legend("right",legend=c("Repulican","Democrat"), pch=19,col=c("Red","Blue"),cex=0.8,bty="n")
```

There are many isolates in the plot, which shrink the size of the network among connected legislators. So I removed all the isolates and plot only connected legislators:

```{r echo=FALSE}
#####Drop Isolates from the data
zz<-which(degree(Network)==0)
matTX<-matrix3[-zz,-zz]
PartyTX<-Party[-zz]
leg.namesTX<-leg.names[-zz]
LeadershipTX<-Leadership[-zz]
RulesTX<-Rules[-zz]
AppropriationsTX<-Appropriations[-zz]
ChamberTX<-Chamber2[-zz]
#SenDistTX<-SenDist[-zz]
#dist.matTX<-dist.mat2[-zz,-zz]
Joint.CommsTX<-Joint.Comms[-zz]
TXid<-rep(1, nrow(matTX))

###Re-designate network
Network2<-network(matTX)
set.vertex.attribute(Network2, "Party", PartyTX)
set.vertex.attribute(Network2, "names", leg.namesTX)
set.vertex.attribute(Network2, "leadership", LeadershipTX)
set.vertex.attribute(Network2, "Appropriations", AppropriationsTX)
set.vertex.attribute(Network2, "Chamber", ChamberTX)
set.vertex.attribute(Network2, "JointComms", Joint.CommsTX)

###
vert.colsTX<-party_color[PartyTX+1]
plot(Network2,vertex.cex=1,edge.col=rgb(150,150,150,50,maxColorValue=255),vertex.col=vert.colsTX,main="Network of Legislative Cosponsorship without Isolates")
legend("right",legend=c("Repulican","Democrat"), pch=19,col=c("Red","Blue"),cex=0.8,bty="n")
```

Github link with data and Rmarkdown code: https://github.com/YaoyaoDai/SocialNetwork-Replication